Automated detections reveal the social information in the changing infant view

### 2020-08-26 writeup-paper/draft_apa_blinded.Rmd
fixing last typos; add to gitignore

From their earliest months, infants are deeply engaged in learning from others. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development; @bruner1975]. And as infants reach their first birthday, they also tend to follow [@yu2013joint; @yu2017hand] and imitate the gestures of their caregivers (e.g., pointing). Infants ability to process these social cues may provide strong scaffolding for early word learning. Longitudinal studies provide some evidence for this link: children’s level of joint engagement with their mother at 9-12 months predicts both their receptive and productive vocabularies [@carpenter1998] and 10 month-olds who follow an adult’s gaze (in an experimental context) have larger vocabularies at 18 months and throughout the second year of life [@brooks2005; @brooks2008]. While the relationship between hand-following and language development has been less well characterized, infants who follow their caregivers’ hands tend to be those who spend more time jointly attending to events with their caregivers [@yu2017hand].

@@

These changes in perspective are likely the downstream consequence of myriad factors, chief of which may be infants' evolving locomotive abilities: an infant's ability to sit, crawl, stand, or walk structures the way they interact with the things and people in their world. Infants' locomotive abilities can change rapidly: the physical body of an infant can lengthen up to 2cm in 24 hours [@lampl1993evidence], leading to changes in their abilities from one day to the next. These motoric developments can be thought of as gateways that open up entirely new phases of development [@iverson2010], causing a cascade of changes in an infant's ability to interact with their world and the people in it [@karasik2014]. Thus, infants’ changing locomotor abilities may shape the social cues that infants' see and seek out, in turn impacting their cognitive and linguistic abilities.

@@

### Accuracy of automated detections 
For face detection, we found that both OpenPose and MTCNN dramatically outperformed ViolaJones (our baseline model) especially with respect to the random sample, where ViolaJones missed many face that were in view (see Table 2). When considering only the composite F-score across all frames, MTCNN slightly outperformed OpenPose  (`r round(perfFacesOverall$f[1],2)` MTCNN vs. `r round(perfFacesOverall$f[2],2)` OpenPose), and MTCNN and OpenPose performed comparably with the random sample. Generally, MTCNN exhibited higher precision, whereas OpenPose exhibited higher recall, and these differences were most pronounced on the randomly sample frames. In other words, while OpenPose generated slightly more false positives than MTCNN, MTCNN missed several faces that were accurately detected by OpenPose. When we restricted our analysis to high-confidence detections from OpenPose (>.5 confidence; default threshold for visualization), we found very high precision (P = `r round(perfFacesOverall$p[3],2)`), but much lower recall (R = `r round(perfFacesOverall$r[3],2)`) and thus overall lower performance (F = `r round(perfFacesOverall$f[3],2)`), indicating that these low-confidence detections often indexed actual faces that were in the infant view.
Figure \ref{fig:exampledetections} shows example successful detections from OpenPose in each age group, and Figure \ref{fig:failures} shows examples of missed faces as well as false positives for context.

@@

### Changes in access to faces and hands 
First, we examined the proportion of face and hand detections as a function of infants' age without considering their posture (see Figure \ref{fig:detByAge}).
While faces tended to be in the field-of-view overall more often than hands, infants' head-mounted cameras were angled slightly upward to capture the presence of faces, and hand detections suffered from somewhat lower recall than face detections. We thus only considered differences in the relative proportion of faces or hands in view as a function of age, posture, and orientation, rather than comparing them directly. Overall, we did not observe strong age related trends from 8-16 months of age; if anything, face detections showed a slight u-shaped pattern, with 12-month-olds having slightly fewer faces in their visual field that 8- or 16-month-olds.

@@

```{r detByPosOrient, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=6, fig.cap = "Proportion of face / wrist detections by children's age, their posture, and their caregivers orientation. Data points are scaled by the amount of time spent in each orientation/posture combination; times when posture/orientation annotatinos were unavaliable or the infant was carried are not plotted. Error bars represent 95\\% bootstrapped confidence intervals"}

@@

In contrast, infant's locomotor developments had a major effect on the faces and hands that were in the field of view (see Figure \ref{fig:detByPosOrient}). Two generalized linear mixed-effect models were used to predict the proportion of faces and hands in view, with orientation, posture, their interaction, and scaled participant's age as fixed effects, and with random slopes for infants' orientation and posture (see all coefficients in Tables 4 and 5). In particular, the interaction between infants' posture and their caregiver's orientation had the most dramatic effect on the social information in view. When caregivers were behind their infants, supporting their infants' sitting or standing positions, infants saw fewer faces. When caregivers were relatively close to their infants, infants who were sitting or standing had more faces in view (Face detections; infant sitting and caregiver (CG) close, b = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Close'),1],2)`, SE  = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Close'),2],2)`, Z = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Close'),3],2)`, `r reportP(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Close'),4])`; infant standing and CG close, b = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Close'),1],2)`, SE  = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Close'),2],2)`, Z = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Close'),3],2)`, `r reportP(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Close'),4])`) than infants who were lying down/crawling (i.e. prone). When caregivers were far away from their infants, face detections were similarity higher (Face detections; infant sitting and CG far, b = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Far'),1],2)`, SE  = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Far'),2],2)`, Z = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Far'),3],2)`, `r reportP(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Far'),4])`; infant standing and CG far, b = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Far'),1],2)`, SE  = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Far'),2],2)`, Z = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Far'),3],2)`,`r reportP(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Far'),4])`).  Infants' age was not significant predictor in accounting for the faces in view (Face detections; Age (scaled), b = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Age (Scaled)'),1],2)`, SE  = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Age (Scaled)'),2],2)`, Z = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Age (Scaled)'),3],2)`, `r reportP(faceGLMOut$coefficients[which(cleanedNames_Int=='Age (Scaled)'),4])`).

>>>>

From their earliest months, infants are deeply engaged in learning from others. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development; @bruner1975]. And as infants reach their first birthday, they also tend to follow [@yu2013joint; @yu2017hand] and imitate the gestures of their caregivers (e.g., pointing). Infants' ability to process these social cues may provide strong scaffolding for early word learning. Longitudinal studies provide some evidence for this link: children’s level of joint engagement with their mother at 9-12 months predicts both their receptive and productive vocabularies [@carpenter1998] and 10 month-olds who follow an adult’s gaze (in an experimental context) have larger vocabularies at 18 months and throughout the second year of life [@brooks2005; @brooks2008]. While the relationship between hand-following and language development has been less well characterized, infants who follow their caregivers’ hands tend to be those who spend more time jointly attending to events with their caregivers [@yu2017hand].

@@

These changes in perspective are likely the downstream consequence of myriad factors, chief of which may be infants' evolving locomotive abilities: an infant's ability to sit, crawl, stand, or walk structures the way they interact with the things and people in their world. Infants' locomotive abilities can change rapidly: the physical body of an infant can lengthen up to 2cm in 24 hours [@lampl1993evidence], leading to changes in their abilities from one day to the next. These motoric developments can be thought of as gateways that open up entirely new phases of development [@iverson2010], causing a cascade of changes in an infant's ability to interact with their world and the people in it [@karasik2014]. Thus, infants’ changing locomotor abilities may shape the social cues that infants see and seek out, in turn impacting their cognitive and linguistic abilities.

@@

### Accuracy of automated detections 
For face detection, we found that both OpenPose and MTCNN dramatically outperformed ViolaJones (our baseline model) especially with respect to the random sample, where ViolaJones missed many faces that were in view (see Table 2). When considering only the composite F-score across all frames, MTCNN slightly outperformed OpenPose  (`r round(perfFacesOverall$f[1],2)` MTCNN vs. `r round(perfFacesOverall$f[2],2)` OpenPose), and MTCNN and OpenPose performed comparably with the random sample. Generally, MTCNN exhibited higher precision, whereas OpenPose exhibited higher recall, and these differences were most pronounced on the randomly sampled frames. In other words, while OpenPose generated slightly more false positives than MTCNN, MTCNN missed several faces that were accurately detected by OpenPose. When we restricted our analysis to high-confidence detections from OpenPose (>.5 confidence; default threshold for visualization), we found very high precision (P = `r round(perfFacesOverall$p[3],2)`), but much lower recall (R = `r round(perfFacesOverall$r[3],2)`) and thus overall lower performance (F = `r round(perfFacesOverall$f[3],2)`), indicating that these low-confidence detections often indexed actual faces that were in the infant view.
Figure \ref{fig:exampledetections} shows example successful detections from OpenPose in each age group, and Figure \ref{fig:failures} shows examples of missed faces as well as false positives for context.

@@

### Changes in access to faces and hands 
First, we examined the proportion of face and hand detections as a function of infants' age without considering their posture (see Figure \ref{fig:detByAge}).
While faces tended to be in the field-of-view overall more often than hands, infants' head-mounted cameras were angled slightly upward to capture the presence of faces, and hand detections suffered from somewhat lower recall than face detections. We thus only considered differences in the relative proportion of faces or hands in view as a function of age, posture, and orientation, rather than comparing them directly. Overall, we did not observe strong age related trends from 8-16 months of age; if anything, face detections showed a slight U-shaped pattern, with 12-month-olds having slightly fewer faces in their visual field than 8- or 16-month-olds.

@@

```{r detByPosOrient, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=6, fig.cap = "Proportion of face / wrist detections by children's age, their posture, and their caregiver's orientation. Data points are scaled by the amount of time spent in each orientation/posture combination; times when posture/orientation annotatinos were unavaliable or the infant was carried are not plotted. Error bars represent 95\\% bootstrapped confidence intervals"}

@@

In contrast, infants' locomotor developments had a major effect on the faces and hands that were in the field of view (see Figure \ref{fig:detByPosOrient}). Two generalized linear mixed-effect models were used to predict the proportion of faces and hands in view, with orientation, posture, their interaction, and scaled participant's age as fixed effects, and with random slopes for infants' orientation and posture (see all coefficients in Tables 4 and 5). In particular, the interaction between infants' posture and their caregiver's orientation had the most dramatic effect on the social information in view. When caregivers were behind their infants, supporting their infants' sitting or standing positions, infants saw fewer faces. When caregivers were relatively close to their infants, infants who were sitting or standing had more faces in view (Face detections; infant sitting and caregiver (CG) close, b = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Close'),1],2)`, SE  = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Close'),2],2)`, Z = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Close'),3],2)`, `r reportP(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Close'),4])`; infant standing and CG close, b = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Close'),1],2)`, SE  = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Close'),2],2)`, Z = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Close'),3],2)`, `r reportP(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Close'),4])`) than infants who were lying down/crawling (i.e. prone). When caregivers were far away from their infants, face detections were similarily higher (Face detections; infant sitting and CG far, b = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Far'),1],2)`, SE  = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Far'),2],2)`, Z = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Far'),3],2)`, `r reportP(faceGLMOut$coefficients[which(cleanedNames_Int=='Sit*Far'),4])`; infant standing and CG far, b = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Far'),1],2)`, SE  = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Far'),2],2)`, Z = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Far'),3],2)`,`r reportP(faceGLMOut$coefficients[which(cleanedNames_Int=='Stand*Far'),4])`).  Infants' age was not significant predictor in accounting for the faces in view (Face detections; Age (scaled), b = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Age (Scaled)'),1],2)`, SE  = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Age (Scaled)'),2],2)`, Z = `r round(faceGLMOut$coefficients[which(cleanedNames_Int=='Age (Scaled)'),3],2)`, `r reportP(faceGLMOut$coefficients[which(cleanedNames_Int=='Age (Scaled)'),4])`).
